%% Example CV - Felipe Duitama
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Felipe Duitama - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Felipe}{Duitama}
\address{Carrera 45 \# 56-51, Bogotá, Colombia}{}{}
\phone[mobile]{+57 320 3448583}
\email{felipedc09@gmail.com}
\extrainfo{\href{https://linkedin.com/in/felipedc09}{LinkedIn}, \href{https://github.com/felipedc09}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Senior Software Engineer with 12+ years building robust, scalable, and maintainable products across complex domains, growing from frontend engineer to technical lead. Core strength in frontend architecture (React, TypeScript, component systems, atomic design) backed by solid Node.js/C\# backend and AWS cloud delivery covering the full lifecycle. Proven at designing complex systems — graph-based routing algorithms, real-time pipelines, AWS microservices, and 3D/AR browser experiences. Comfortable owning architecture decisions, leading cross-functional teams, and going hands-on when it matters.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Frontend Architecture}: React, Next.js, TypeScript, component systems, atomic design, TypeScript migrations, WebGL, Chart.js, Mapbox.

\item \textbf{Backend \& Cloud}: Node.js, C\#/.NET, AWS microservices (ECS Fargate, EC2, Lambda, API Gateway, CloudWatch), custom message brokers.

\item \textbf{Algorithms \& Systems}: Graph-based routing (Dijkstra), real-time data pipelines, file-conversion pipelines, WebSocket services.

\item \textbf{3D / AR}: Unity 3D, Microsoft HoloLens SDK, browser-native 3D (WebGL), BIM/Revit plugin development (C\#).

\item \textbf{DevOps \& Tooling}: CI/CD (GitHub Actions), Docker, Kubernetes, Playwright/Cypress testing, AI-assisted development (LLM coding agents, MCP, Claude Code).

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{2013--Present}{Software Engineer $\rightarrow$ Technical Lead}{3D Virtual Environment Solutions}{Bogotá, Colombia}{}{\vspace{1pt}
\begin{itemize}
    \item Led migration of the ARAS/BIMEP HVAC platform from a vanilla-JS monolith to React + TypeScript + Node.js, then architected the transition to AWS microservices (ECS Fargate, EC2, API Gateway), decomposing compute-intensive algorithms into independently scalable services.
    \item Designed and implemented a Dijkstra-based pipe auto-routing algorithm over a room-grid graph where edge weights encode HVAC heat load, automating layout-aware pipe distribution across building floors.
    \item Built a lightweight custom message broker coordinating async communication between Node.js services and Python algorithms on AWS Lambda; established CI/CD via GitHub Actions with semantic versioning.
    \item Served as technical lead during algorithm integration: owned architecture and infrastructure decisions, ran planning, managed the backlog in Notion, and coordinated a cross-functional team across engineering, design, and data science.
    \item Delivered multiple products end-to-end: a facility-mapping tool (React, Next.js, PostgreSQL, Mapbox), a browser-native 3D model viewer with a file-conversion pipeline and WebSocket progress, and a hospital-scale digital twin (Unity 3D, MENU stack) integrating live HVAC sensor data.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2011--2020}{Systems Engineering}{Universidad Distrital Francisco José de Caldas}{Bogotá, Colombia}{}{\vspace{1pt}
Software engineering, algorithms, and systems design.
}}

\vspace{3pt}

\item{\cventry{2017--2019}{Unity Certified Developer}{Unity Technologies}{}{}{\vspace{1pt}
Certified in Unity 3D development.
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (intermediate, B1--B2, improving toward C1), French (basic).
\end{itemize}

% ============================================================
%     CONFERENCES
% ============================================================

\section{Conferences}
\vspace{1pt}
\begin{itemize}
\item JSConf, NodeConf, Unity Developer Day (2019); CSSConf Colombia (2021).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
